On Secure Delegation of SampBQP with a Classical Client

### 2019-11-21 preliminaries.tex
Add different definitions of QPIP

We then define a model of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.

\begin{definition}
	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

>>>>

We then define models of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	TODO Fix/redefine this to allow $\bbV$ a single qubit and ability to ONLY measure in X/Z
	\begin{itemize}
		\item $\bbP$ is a hybrid quantum-classical machine. Its classical part is a $BPP$ machine. Its quantum part is a register of a single qubit, on which the verifier can apply $X$ or $Z$ measurements.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ defined in the same way as in $\QPIP_{XZ}$ except that $\bbV$ is fully classical and cannot receive or measure qubits.
\end{definition}

\begin{theorem}
	$\QPIP_{XZ}=\QPIP_0$
\end{theorem}
\begin{proof}
	See \cite{mahadev_delegation}.
\end{proof}
